Potential of I/O Aware Workflows in Climate and Weather

### 2020-05-22 paper.tex
Figure changes / grayscaling for "irrelevant" elements.

\usepackage{array}
\usepackage{todonotes}
\usepackage[capitalize]{cleveref}
\Crefname{lstlisting}{Listing}{Listings}
\usepackage{subcaption}
\usepackage{comment}
\usepackage{float}
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage{textcomp} %for upquote=true (straight quotes)
\definecolor{pblue}{rgb}{0.13,0.13,1}
\definecolor{pgreen}{rgb}{0,0.5,0}
\definecolor{pred}{rgb}{0.9,0,0}
\definecolor{pgrey}{rgb}{0.46,0.45,0.48}
\lstset{
    basicstyle=\ttfamily\footnotesize,
    numberstyle=\ttfamily\tiny,
    frame=single,
    numbers=left,
    numbersep=1em,
    xleftmargin=2em,
    language=XML, % to avoid type being blue
    breaklines=true,
    breakatwhitespace=true,
    postbreak=\hbox{$\hookrightarrow$ },
    showstringspaces=false,
    tabsize=2,
    commentstyle=\color{pgreen},
    keywordstyle=\color{pblue},
    stringstyle=\color{pred},
    moredelim=[il][\textcolor{pgrey}]{\[\]},
    moredelim=[is][\textcolor{pgrey}]{\%\%}{\%\%},
  columns=fullflexible,
    upquote=true
}

@@

\fig{width=0.8\columnwidth}{pic/cylc1}{Example of a Cylc workflow with its configuration file}

@@

\begin{figure}[b]
    \begin{minipage}{.42\linewidth}
        \centering
        \includegraphics[width=0.42\textwidth]{pic/layers-xios}
        \subcaption{I/O path for an MPI-parallel application}\label{pic/layers-xios}
    \end{minipage}
    \begin{minipage}{.58\linewidth}
        \centering
        \includegraphics[width=1\textwidth]{pic/system}
        \subcaption{Example of an heterogeneous HPC landscape}\label{pic/system}
    \end{minipage}
    \vspace{5pt}
    \caption{Typical hardware and software environment for applications}
    \label{fig:34}
\end{figure}

>>>>

\usepackage{array}
\usepackage{todonotes}
\usepackage[capitalize]{cleveref}
\Crefname{lstlisting}{Listing}{Listings}
\usepackage{subcaption}
\usepackage{comment}
\usepackage{float}
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage{textcomp} %for upquote=true (straight quotes)
\definecolor{pblue}{rgb}{0.13,0.13,1}
\definecolor{pgreen}{rgb}{0,0.5,0}
\definecolor{pred}{rgb}{0.9,0,0}
\definecolor{pgrey}{rgb}{0.46,0.45,0.48}
\lstset{
    basicstyle=\ttfamily\footnotesize,
    numberstyle=\ttfamily\tiny,
    frame=single,
    numbers=left,
    numbersep=1em,
    xleftmargin=2em,
    language=XML, % to avoid type being blue
    breaklines=true,
    breakatwhitespace=true,
    postbreak=\hbox{$\hookrightarrow$ },
    showstringspaces=false,
    tabsize=2,
    commentstyle=\color{pgreen},
    keywordstyle=\color{pblue},
    stringstyle=\bfseries,
    moredelim=[il][\textcolor{pgrey}]{\[\]},
    moredelim=[is][\textcolor{pgrey}]{\%\%}{\%\%},
  columns=fullflexible,
    upquote=true
}

@@

\fig{width=0.8\columnwidth}{pic/cylc1}{Example of a Cylc workflow with its configuration file \cite{8675433}}

@@

\begin{figure}[b]
    \begin{minipage}{.42\linewidth}
        \centering
        \includegraphics[width=0.42\textwidth]{pic/layers-xios}
        \subcaption{I/O path for an MPI application}\label{pic/layers-xios}
    \end{minipage}
    \begin{minipage}{.58\linewidth}
        \centering
        \includegraphics[width=1\textwidth]{pic/system}
        \subcaption{Example of an heterogeneous HPC landscape}\label{pic/system}
    \end{minipage}
    \vspace{5pt}
    \caption{Typical hardware and software environment for applications}
    \label{fig:34}
\end{figure}
